%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/katetreadwell}{\Large Kate Treadwell}} & Email : \href{mailto:ktreadwell11@gmail.com}{ktreadwell11@gmail.com}\\
  \href{https://www.linkedin.com/in/katetreadwell}{https://www.linkedin.com/in/katetreadwell/} & Mobile: 720-951-5335 \\
\end{tabular*}

 %-----------EDUCATION-----------------
\section{Summary}
  \resumeSubHeadingListStart
  {Analytics professional passionate about empowering teams to make well-informed, data-driven decisions. Proven leader and strategic partner in developing long-term plans for success. Strong foundation in technology and business applications. Teacher, developer, and mentor of team members and the community. Significant experience in large-scale and enterprise level analytics and big data. Focused on helping companies find the best possible path based on research and quantitative metrics.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Strava}{Denver, CO}
      {Senior Product Analyst}{April 2018 - April 2019}
      \resumeItemListStart
        \resumeItem{}
          {Analytics leader on 14 person cross-functional product team which was responsible for building new revenue streams for the company, managing product surfaces available to 83 million athletes, and planning novel ways to increase value for athletes, Strava, and partners.}
        \resumeItem{}
          {Built internal attribution model resulting in the ability to provide exact numbers for new user acquisition. At least 2 new contracts in under 3 months were signed using this data which brought over over 2 million in new revenue.}
        \resumeItem{}
          {Conducted and analyzed A/B tests for all new potential product surfaces to include testing for significance, cohort sizing, adding required instrumentation, and documenting detailed results.}
        \resumeItem{}
          {Developed over 10 new performance metrics for product and sales team to include both executive metrics and team-level metrics resulting in the measurement of the product for the first time in team history.}
        \resumeItem{}
          {Worked consistently with tables over 3TB each in a 300+ table data warehouse in order to discover novel insights which drove product development.}
        \resumeItem{}
          {Worked with entire company (180+) to develop and implement Tableau and Tableau Server to include: training, strategy, office hours, and data governance.}
        \resumeItem{}
          {One of the first 15 founding members of Denver HQ. Leader in recruiting, social team, and on-boarding team for new hires.}
        \resumeItem{}
          {Worked with multiple external partners and media outlets to develop reporting and external brand insights for our product.}
        \resumeItem{}
          {Won 3 internal rewards for excellence (Kudos Coins).}
      \resumeItemListEnd

    \resumeSubheading
      {InterWorks, Inc.}{San Francisco, CA}
      {Principle Business Intelligence Consultant / Internal Analytics Practice Lead}{August 2012 - April 2018}
      \resumeItemListStart
        \resumeItem{}
          {Lead multiple teams of up to 10 people across various geographic locations to include DC, San Francisco, and Denver over a 6 year period.}
        \resumeItem{}
          {Co-authored ``Tableau Your Data! Fast and Easy Visual Analysis with Tableau Software" (Edition I and II).}
        \resumeItem{}
          {Managed all levels of InterWorks' internal analytics practice, from ETL to database administration, report development, and integration.}
        \resumeItem{}
          {Worked with myriad of clients across multiple verticals including technology, education, marketing, banking, government, public policy, and retail.}
        \resumeItem{}
          {Tableau developer and trainer, lead Tableau Server and Tableau Desktop classes at all levels of student experience.}
        \resumeItem{}
          {Managed projects ranging from data capture, architecture, retrieval best practices, ETL, analytics, Tableau development, and visual best practices.}
        \resumeItem{}
          {Developed, designed, and optimized data structures for analysis.}
        \resumeItem{}
          {Built data pipelines for multiple data sources, including Salesforce, Pardot, Strava, HubSpot, Facebook, and Google Analytics.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Red Ball Oxygen}{Shreveport, LA}
      {Chief Technology Officer}{May 2009 - June 2012}
      \resumeItemListStart
        \resumeItem{}
          {Lead internal IT team, external consultants, and vendors.}
        \resumeItem{}
          {Collaborated with company president to develop the five-year strategic operations and corporate BI practice plan.}
        \resumeItem{}
          {Established 40 KPIs for financial, operational, and sales goals, increasing compliance on one KPI from 40\% to 92.5\% in less than six months.}
        \resumeItem{}
          {Lead multiple projects with 5-15 person teams tasked with developing and steering operations and obtaining operational improvements.}
        \resumeItem{}
          {Developed and architected first data warehouse in company history.}
        \resumeItem{}
          {Built ETL pipeline for data warehouse which included moving data from multiple sources to MSSQL.}
        \resumeItem{}
          {Introduced Tableau which transformed the way data was used to solve problems and improve data analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {Kansas City Southern Railway}{Shreveport, LA}
      {Program Manager}{June 2008 - May 2009}
      \resumeItemListStart
        \resumeItem{}
          {Managed locomotive capital improvement projects and led system-wide team to meet the logistical needs of 556 locomotives.}
        \resumeItem{}
          {Improved tracking of locomotive material expenses by 100\%.}
        \resumeItem{}
          {Reduced average wait time for locomotive materials by 50\%.}
         \resumeItem{}
          {Implemented KPIs for logistics cell, achieving 100\% increase in tracking all indicators.}
      \resumeItemListEnd
      
    \resumeSubheading
      {United States Army}{Ft. Polk, LA}
      {Captain}{May 2004 - May 2008}
      \resumeItemListStart
        \resumeItem{\textbf{Brigade Adjutant - Captain:}}
          {Lead 10-person team responsible for personnel management, evaluations, promotions, finance, legal, leadership development and administrative support for 760-person brigade at Joint Readiness Training Center.}
        \resumeItem{\textbf{Chief, Division Plans and Operations - Captain}:}
          {Led 20 teams in developing, planning, and executing personnel support services for 49 units with over 7,000 Soldiers at Ft. Polk, LA.}
    \resumeItem{\textbf{Detachment Executive Officer - Lieutenant}:}
          {Second in command of 50-person personnel services detachment in Iraq.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{}{Data Strategy, Data Architecture, Data Accessibility, Big Data Management, Cloud Data, Python, Plotly, Pandas, Tableau, Looker, Snowflake, MSSQL, MySQL, Redshift, Exasol, ETL Tools, Excel/Sheets, Git, Data Visualization, XML, JSON, YAML}
     \item{}{Familiarity with: Airflow, Luigi, R, \LaTeX}
    }
  \resumeSubHeadingListEnd
%\section{Soft Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{}{Problem Solving, Decision Making, Business %Acumen, Strategic Development, Process Improvement, Leadership, %Mentorship, Project Management/Planning, Change Management, COE %Implementation, Training }}
%  \resumeSubHeadingListEnd
  
 %-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Louisiana State University - Shreveport}{Shreveport, LA}
      {MBA}{September 2009 - December 2011}
          \resumeSubheading
      {DePaul University}{Chicago, IL}
      {Bachelor of Arts in International Studies}{September 2000 - June 2004}
  \resumeSubHeadingListEnd
  
  %-----------EDUCATION-----------------
\section{References - More upon request}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michael Horvath - Co-Founder}{Strava}
      {603.369.1779 - michael@strava.com}{}
    \resumeSubheading
      {Kelsey Robb - Marketing Analytics Department Head}{Windstream}
      {303.895.9518 - kelsey.robb@gmail.com}{}
    \resumeSubheading
      {Logan Medina - Web Engineer}{Strava}
      {510.320.0331 - lmedina@strava.com}{}
  \resumeSubHeadingListEnd
  
\end{document}
